Research on The Impact of Past Behaviour Normality on Regret

### 2024-02-15 outputs/paper/paper.qmd
result added
results of the two experiments added, discussion section structure completed

In academic terms, the disparity in responses suggests that individuals who engage in behaviors that are not typical for them (Mr. Jones) are more likely to experience and be perceived as having stronger regret and more negative emotional responses. The consistency in this pattern across different measures indicates a robust finding, aligning with psychological theories that predict increased emotional consequences for actions that deviate from one's own or society's expectations. The bar plot @fig-experiment1bar quantitatively illustrates these findings. Mr. Jones's experiences with regret and negative affect are visually represented by significantly taller bars compared to Mr. Smith's, reflecting the numerical data.

@@

@@

## First discussion point

## Second discussion point

## Third discussion point

## Weaknesses and next steps

>>>>

The disparity in responses suggests that individuals who engage in behaviors that are not typical for them (Mr. Jones) are more likely to experience and be perceived as having stronger regret and more negative emotional responses. The consistency in this pattern across different measures indicates a robust finding, aligning with psychological theories that predict increased emotional consequences for actions that deviate from one's own or society's expectations. The bar plot @fig-experiment1bar quantitatively illustrates these findings. Mr. Jones's experiences with regret and negative affect are visually represented by significantly taller bars compared to Mr. Smith's, reflecting the numerical data.

@@

@tbl-experiment2 and @fig-experiment2bar illustrate the outcomes of experiment 2, which addresses perceptions of regret and luck in decision-making under varying conditions of routine and exception.

Mr. Adams, who represents routine behavior, exhibits a regret level of 18.8%, suggesting that participants view routine actions as less regrettable. His luck perception stands at 32.9%, indicating that participants may see routine choices as less influenced by luck. On the contrary, Mr. White, who represents an exception to routine, is associated with a markedly higher regret level at 81.2%. This suggests that non-routine actions are perceived as significantly more regrettable. Furthermore, his luck perception is at 67.1%, which could reflect a belief that deviations from routine are more susceptible to chance and less within an individual's control.

@fig-experiment2bar graphically accentuates these findings, with much higher height bars for Mr.White in terms of regret and luck. This visual comparison conveys the statistical differences and underscores the paper's exploration of the psychological impacts of routine versus exceptional decisions. This visualization complements the statistical data by providing an immediate, comparative view of the emotional weight and perceived randomness assigned to each individual's experience.

@@

## Replication and estimand

## Measurement validity

## Ethical Considerations and Bias

## Limitations and Future Research

## Conclusion
